\section{Introduction}
\subsection{Purpose}
This document specifies the software requirements for the AI-Powered Retail Shop Management System. It provides a detailed, formal, and testable description of the system for stakeholders including project supervisors, developers, testers, and future maintainers.

\subsection{Document Conventions}
Requirements use the word \textit{shall} to indicate a mandatory requirement, \textit{should} for recommended behavior, and \textit{may} for optional behavior. Each requirement is written in clear, simple English to support testing and verification.

\subsection{Intended Audience and Reading Suggestions}
Project supervisors and management should focus on Sections II and III for scope, users, and overall context. Developers and testers should focus on Sections IV and V for detailed functional and non-functional requirements. System administrators should read Sections III, IV, and VI for interfaces, security, and operational constraints.

\subsection{Product Scope}
The system is a web-based retail management platform that provides inventory, billing, sales reporting, and an LLM-driven assistant. Users can query business data using natural language, generate automated reports, and receive recommendations. The system targets small and medium retail businesses that need operational efficiency and intelligent decision support.

\subsection{References}
\begin{itemize}
    \item IEEE Std 830-1998, IEEE Recommended Practice for Software Requirements Specifications.
    \item ISO/IEC/IEEE 29148:2018, Systems and software engineering --- Life cycle processes --- Requirements engineering.
\end{itemize}
