\section{Overall Description}
\subsection{Product Perspective}
The system is a new product composed of a web frontend, a backend API layer, a PostgreSQL database, and an AI layer that uses the OpenAI API with Retrieval-Augmented Generation (RAG). The system is designed as a modular service-oriented architecture with clear separation between presentation, business logic, data storage, and AI services.

\subsection{Product Functions}
High-level functions include:
\begin{itemize}
    \item Manage products, categories, units, suppliers, and stock levels.
    \item Create and manage invoices and POS transactions.
    \item Track sales and generate operational and analytical reports.
    \item Provide a conversational assistant for data queries and insights.
    \item Generate automated insights and recommendations.
\end{itemize}

\subsection{User Classes and Characteristics}
\begin{itemize}
    \item Owner/Manager: Full access to inventory, billing, reporting, and AI insights.
    \item Cashier: Access to POS and invoice generation; limited reporting.
    \item Analyst: Access to reporting and insights; no inventory editing.
    \item System Admin: Configuration, user management, and audit review.
\end{itemize}

\subsection{Operating Environment}
\begin{itemize}
    \item Web client: modern browsers (Chrome, Edge, Firefox).
    \item Server: Node.js/Express runtime on Linux or Windows.
    \item Database: PostgreSQL 13+.
    \item AI layer: OpenAI API with HTTPS access.
\end{itemize}

\subsection{Design and Implementation Constraints}
\begin{itemize}
    \item The system shall comply with data privacy regulations applicable to the deployment region.
    \item Internet connectivity is required for OpenAI API access.
    \item Responses must be derived from authorized data using RAG retrieval rules.
    \item The system shall be deployable on commodity hardware.
\end{itemize}

\subsection{User Documentation}
The project will provide a user guide, quick-start handbook, and admin configuration guide.

\subsection{Assumptions and Dependencies}
\begin{itemize}
    \item Accurate data entry by staff for inventory and sales.
    \item Availability of OpenAI API keys and stable network connectivity.
    \item PostgreSQL database is accessible to the backend.
\end{itemize}
