\section{Functional Requirements}
\subsection{Inventory Management}
\begin{itemize}
    \item The system shall allow users to add, edit, and deactivate products.
    \item The system shall track stock quantity, reorder level, cost price, and selling price.
    \item The system shall support batch import of products using CSV.
    \item The system shall generate low-stock alerts and show them on the dashboard.
    \item The system shall support product categories, brands, and units of measure.
\end{itemize}

\subsection{Billing and POS}
\begin{itemize}
    \item The system shall create sales invoices with unique invoice numbers.
    \item The system shall support discounts and taxes per item or invoice.
    \item The system shall update stock quantities after successful billing.
    \item The system shall support multiple payment methods (cash, card, UPI).
    \item The system shall support invoice cancellation with audit logging.
\end{itemize}

\subsection{Sales Tracking and Reporting}
\begin{itemize}
    \item The system shall record each transaction with timestamp, items, totals, and cashier.
    \item The system shall generate daily, weekly, and monthly sales reports.
    \item The system shall allow report export in PDF and CSV formats.
    \item The system shall support filtering by product, category, and date range.
\end{itemize}

\subsection{LLM Assistant and Natural Language Queries}
\begin{itemize}
    \item The system shall provide a chat interface for natural-language queries.
    \item The system shall translate user queries into structured queries (e.g., SQL).
    \item The system shall use RAG to retrieve relevant data before generating answers.
    \item The system shall display the data source or evidence used in answers.
    \item The system shall handle ambiguous queries by requesting clarification.
    \item The system shall block responses to unauthorized data based on user role.
\end{itemize}

\subsection{Automated Insights}
\begin{itemize}
    \item The system shall generate insights such as top-selling products and slow movers.
    \item The system shall recommend restocking for low-velocity items based on trends.
    \item The system shall detect unusual sales drops or spikes.
    \item The system shall allow scheduling of insight reports by email.
\end{itemize}

\subsection{User and Role Management}
\begin{itemize}
    \item The system shall support role-based access control.
    \item The system shall allow administrators to create, deactivate, and reset users.
    \item The system shall log user actions for auditing.
    \item The system shall enforce password complexity rules.
\end{itemize}
