\section{Non-Functional Requirements}
\subsection{Performance}
\begin{itemize}
    \item Standard page loads shall complete within 3 seconds under normal load.
    \item LLM responses should be returned within 10 seconds for typical queries.
    \item Report generation for one month of data shall complete within 15 seconds.
\end{itemize}

\subsection{Security}
\begin{itemize}
    \item The system shall require authentication for all non-public endpoints.
    \item Passwords shall be stored using strong hashing (bcrypt or equivalent).
    \item The system shall log access to sensitive data.
    \item The system shall enforce role-based access control for all data queries.
\end{itemize}

\subsection{Reliability and Availability}
\begin{itemize}
    \item The system shall be available 99\% of business hours.
    \item The system shall back up the database daily.
    \item The system shall provide recovery procedures for failed transactions.
\end{itemize}

\subsection{Maintainability}
\begin{itemize}
    \item The system shall follow modular architecture to allow feature extension.
    \item The system shall include API documentation and inline code comments for complex logic.
    \item The system shall provide configuration via environment variables.
\end{itemize}

\subsection{Usability}
\begin{itemize}
    \item The system shall provide consistent UI labels and error messages.
    \item The system shall provide help tips for the assistant feature.
    \item The system shall support keyboard navigation for the POS screen.
\end{itemize}

\subsection{Scalability}
\begin{itemize}
    \item The system shall support at least 20 concurrent POS sessions.
    \item The system shall handle growth to 100,000 product records without redesign.
\end{itemize}

\subsection{Data Quality and Explainability}
\begin{itemize}
    \item The system shall show data sources used by the assistant response.
    \item The system shall mark AI responses as advisory, not authoritative.
\end{itemize}
